---
title: "Introduction to indagridat"
author: "Simon Moulds"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to indagridat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

In recent decades India has experienced substantial environmental change. Various sources of data in various locations document this change, but they have several limitations. In this package we provide two datasets in a consistent format...

# Examples

One of the best ways to use this package is for visualisation. For this we use the `spacetime` package.

```{r}
library(indagridat)

data(indiastat1950)
data(icrisat1950)
```










<!--
## Styles
-->

<!--
The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css
-->

<!--
## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.
-->
